---
title: "COD_20241025_science_wide_author_database.rmd"
author: "Minsik Kim"
date: "2024-10-21"
output:
    rmdformats::downcute:
        downcute_theme: "chaos"
        code_folding: hide
        fig_width: 6
        fig_height: 6
        df_print: paged
#mainfont: Times New Roman
editor_options: 
  chunk_output_type: inline
---

<style>
  /* Default light mode styles */
  .reactable {
    background-color: #ffffff !important; /* Light background */
    color: #000000 !important;            /* Dark text */
    border-color: #cccccc !important;     /* Light border */
  }

</style>

<style>
  body {
    font-family: "Times New Roman", serif;
  }
</style>

## Loading packages

```{r setup, warning = FALSE}
#===============================================================================
#BTC.LineZero.Header.1.1.0
#===============================================================================
#R Markdown environment setup and reporting utility.
#===============================================================================
#RLB.Dependencies:
#   knitr, magrittr, pacman, rio, rmarkdown, rmdformats, tibble, yaml
#===============================================================================
#Input for document parameters, libraries, file paths, and options.
#=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=


path_working <- 
        ifelse(sessionInfo()[1]$R.version$platform == "x86_64-pc-linux-gnu",
               "/mnt/4T_samsung/Dropbox/",
               ifelse(sessionInfo()[1]$R.version$platform == "aarch64-apple-darwin20",
                      "/Volumes/macdrive/Dropbox/", 
                      "/Users/minsikkim/Dropbox (Personal)/"))
path_library <- 
        ifelse(sessionInfo()[1]$R.version$platform == "x86_64-pc-linux-gnu",
               "/home/bagel/R_lib/",
               "/Library/Frameworks/R.framework/Resources/library/")


str_libraries <- c("readxl", "phyloseq", "tidyverse", "pacman", "yaml",
                   "DESeq2",
                   "ggplot2", "vegan", "microbiome","ggpubr", "viridis",
                   "decontam", "gridExtra", "ggpubr", "lme4", "lmerTest",
                   "writexl", "harrietr", "Maaslin2", "ggtext", "mgcv",
                   "ggpmisc", "janitor", "breakaway", "decontam",
                   "reactablefmtr", "DT", "htmltools", "bugphyzz")
        
YAML_header <-
'---
title: "COD_20241025_science_wide_author_database.rmd"
author: "Minsik Kim"
date: "2024.10.25"
output:
    rmdformats::downcute:
        downcute_theme: "chaos"
        code_folding: hide
        fig_width: 11
        fig_height: 11
---'

seed <- "20241025"

#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
#Loads libraries, file paths, and other document options.
#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
FUN.LineZero.Boot <- function() {
    .libPaths(path_library)

    require(pacman)
    pacman::p_load(c("knitr", "rmarkdown", "rmdformats", "yaml"))

    knitr::opts_knit$set(root.dir = path_working)

    str_libraries |> unique() |> sort() -> str_libraries
    pacman::p_load(char = str_libraries)

    set.seed(seed)
}

FUN.LineZero.Boot()
#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
#Outputs R environment report.
#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
FUN.LineZero.Report <- function() {
    cat("Line Zero Environment:\n\n")
    paste("R:", pacman::p_version(), "\n") |> cat()
    cat("Libraries:\n")
    for (str_libraries in str_libraries) {
        paste(
            "    ", str_libraries, ": ", pacman::p_version(package = str_libraries),
            "\n", sep = ""
        ) |> cat()
    }
    paste("\nOperating System:", pacman::p_detectOS(), "\n") |> cat()
    paste("    Library Path:", path_library, "\n") |> cat()
    paste("    Working Path:", path_working, "\n") |> cat()
    paste("Seed:", seed, "\n\n") |> cat()
    cat("YAML Header:\n")
    cat(YAML_header)
}
FUN.LineZero.Report()

```

# Description of fields

```{r warning=FALSE}


read_excel("Git/lectures_etc/Table_1_Authors_career_2023_pubs_since_1788_wopp_extracted_202408.xlsx") %>%
        reactable::reactable(sortable = T, searchable = T, showPageSizeOptions = T)

```


# Data analysis

## Loading data

### Raw data - affiliated with Korean institution

```{r warning=FALSE}

data_raw <- read_excel("Git/lectures_etc/Table_1_Authors_career_2023_pubs_since_1788_wopp_extracted_202408.xlsx", sheet = 2)

data_raw %>%
        subset(., .$cntry == "kor") %>%
        reactable::reactable(sortable = T, searchable = T, showPageSizeOptions = T)

```

### Summary statistics: Korean institution's average rank and number of researchers

```{r}
data_raw %>%
        #subset(., .$cntry == "kor") %>%
        
        group_by(inst_name) %>%
        mutate(University = ifelse(grepl("University|university|School|Yonsei|Institute of Science and Technology", inst_name), "University", "Non-university"),
               .before = "inst_name") %>%
        mutate(inst_name = case_when(grepl("Daegu Gyeongbuk Institute of Science and Technology", inst_name)~"DGIST", 
                                     grepl("Gwangju Institute of Science and Technology", inst_name)~"GIST", 
                                     grepl("Korea Advanced Institute of Science and Technology", inst_name)~"KAIST", 
                                     grepl("Ulsan National Institute of Science and Technology", inst_name)~"UNIST", 
                                     grepl("Seoul National University", inst_name)~"Seoul National University",
                                     grepl("Yonse", inst_name)~"Yonsei University", 
                                     .default = inst_name)) %>%
        summarise(University = min(University),
                  `Average rank` = mean(rank) %>% round(2), `SD rank` = sd(rank) %>% round(2), `Number of researchers` = n()) %>% 
        
        #subset(., .$`Number of researchers`> 10) %>% 
        mutate(`Rank of institution's mean rank (ROK)` = rank(`Average rank`, ,ties.method = "min"),
               `Rank of institution's number of researchers (ROK)` = rank(`Number of researchers`,ties.method = "max")) %>%
        reactable::reactable(sortable = T, searchable = T, showPageSizeOptions = T, groupBy = c("University") )
```

### Matrices of Korean Universities

```{r}

data_raw %>%
        subset(., .$cntry == "kor") %>%
        group_by(inst_name) %>%
        mutate(University = ifelse(grepl("University|university|School|Yonsei|Institute of Science and Technology", inst_name), "University", "Non-university"),
               .before = "inst_name") %>%
        mutate(inst_name = case_when(grepl("Daegu Gyeongbuk Institute of Science and Technology", inst_name)~"DGIST", 
                                     grepl("Gwangju Institute of Science and Technology", inst_name)~"GIST", 
                                     grepl("Korea Advanced Institute of Science and Technology", inst_name)~"KAIST", 
                                     grepl("Ulsan National Institute of Science and Technology", inst_name)~"UNIST", 
                                     grepl("Seoul National University", inst_name)~"Seoul National University",
                                     grepl("Yonse", inst_name)~"Yonsei University", 
                                     .default = inst_name)) %>%
        summarise(#University = min(University),
                  `Number of researchers` = , 
                  `Average H-index` = mean(h23) %>% round(2), 
                  `Average #papers` = mean(np6023) %>% round(2),
                  `Average #citations` = mean(`nc9623 (ns)`) %>% round(2)
                  ) %>% 
        reactable::reactable(sortable = T, searchable = T, showPageSizeOptions = T)


```


### Correlation between instituion size and average rank in Korea

```{R}
data_raw %>%
        subset(., .$cntry == "kor") %>%
        group_by(inst_name, `sm-field`) %>%
        mutate(University = ifelse(grepl("University|university|School|Yonsei|Institute of Science and Technology", inst_name), "University", "Non-university"),
               .before = "inst_name") %>%
        
        mutate(inst_name = case_when(grepl("Daegu Gyeongbuk Institute of Science and Technology", inst_name)~"DGIST", 
                                     grepl("Gwangju Institute of Science and Technology", inst_name)~"GIST", 
                                     grepl("Korea Advanced Institute of Science and Technology", inst_name)~"KAIST", 
                                     grepl("Ulsan National Institute of Science and Technology", inst_name)~"UNIST", 
                                     grepl("Seoul National University", inst_name)~"Seoul National University",
                                     grepl("Yonse", inst_name)~"Yonsei University", 
                                     .default = inst_name)) %>%
        summarise(University = min(University),
                  Field = min(`sm-field`),
                  `Average rank` = mean(rank) %>% round(2), `SD rank` = sd(rank) %>% round(2), `Number of researchers` = n()) %>% 
        mutate(`Institution with < 5 researchers` = ifelse(`Number of researchers`< 5, "Under 5 researchers per Institution", "Over 5 researchers per Institution")) %>%
        ggplot(., aes(x = `Number of researchers`, y = `Average rank`, col = University)) +
        geom_point() +
        theme_classic() +
        MetBrewer::scale_color_met_d(name = "VanGogh2") + 
        theme(legend.position = "top") +
        scale_y_log10() +
        facet_wrap(~`Institution with < 5 researchers`, scales = "free") +
        geom_smooth(method = "lm")
        #geom_text(aes(label = inst_name)) +
        #ggrepel::geom_text_repel(aes(label = inst_name))
        
        
        

```
### Correlation between instituion size and average rank in Korea - by field

```{R}
data_raw %>%
        subset(., .$cntry == "kor") %>%
        group_by(inst_name, `sm-field`) %>%
        mutate(University = ifelse(grepl("University|university|School|Yonsei|Institute of Science and Technology", inst_name), "University", "Non-university"),
               .before = "inst_name") %>%
        
        mutate(inst_name = case_when(grepl("Daegu Gyeongbuk Institute of Science and Technology", inst_name)~"DGIST", 
                                     grepl("Gwangju Institute of Science and Technology", inst_name)~"GIST", 
                                     grepl("Korea Advanced Institute of Science and Technology", inst_name)~"KAIST", 
                                     grepl("Ulsan National Institute of Science and Technology", inst_name)~"UNIST", 
                                     grepl("Seoul National University", inst_name)~"Seoul National University",
                                     grepl("Yonse", inst_name)~"Yonsei University", 
                                     .default = inst_name)) %>%
        summarise(University = min(University),
                  Field = min(`sm-field`),
                  `Average rank` = mean(rank) %>% round(2), `SD rank` = sd(rank) %>% round(2), `Number of researchers` = n()) %>% 
        ggplot(., aes(x = `Number of researchers`, y = `Average rank`, col = Field)) +
        geom_point() +
        theme_classic() +
        #MetBrewer::scale_color_met_d(name = "Signac") +
        theme(axis.text.x = element_blank(),
              axis.text.y = element_blank()) +
        scale_y_log10() +
        facet_wrap(~Field,scales = "free_x") +
        geom_smooth(method = "lm")
        #geom_text(aes(label = inst_name)) +
        #ggrepel::geom_text_repel(aes(label = inst_name))
        
        
        

```
### Korean Institutions

```{r}


data_raw %>%
        subset(., .$cntry == "kor") %>%
        mutate(University = ifelse(grepl("University|university|School|Yonsei|Institute of Science and Technology", inst_name), "University", "Non-university"),
               .before = "inst_name") %>%
        mutate(inst_name = case_when(grepl("Daegu Gyeongbuk Institute of Science and Technology", inst_name)~"DGIST", 
                                     grepl("Gwangju Institute of Science and Technology", inst_name)~"GIST", 
                                     grepl("Korea Advanced Institute of Science and Technology", inst_name)~"KAIST", 
                                     grepl("Ulsan National Institute of Science and Technology", inst_name)~"UNIST", 
                                     grepl("Seoul National University", inst_name)~"Seoul National University",
                                     grepl("Yonse", inst_name)~"Yonsei University", 
                                     .default = inst_name)) %>%
        group_by(inst_name) %>%
        summarise(authfull = authfull,
                  papers = np6023,
                  citation =`nc9623 (ns)`,
                  h = `h23 (ns)`,
                  University = min(University),
                  Field = min(`sm-field`),
                  `Average rank` = mean(rank) %>% round(2), `SD rank` = sd(rank) %>% round(2), `Number of researchers` = n()) %>% 
        ungroup() %>%
        mutate(`Inha University` = ifelse(.$inst_name == "Inha University", "Inha University", "Others"),
               inha_researcher = ifelse(.$inst_name == "Inha University", authfull, NA)) %>%
        subset(., .$`Number of researchers` > 40) %>%
        ggplot(., aes(x = papers, y = citation, col = `Inha University`)) +
        
        geom_point() +
        theme_classic() +
        MetBrewer::scale_color_met_d(name = "Egypt") +
        theme(legend.position = "top") +
        #      axis.text.y = element_blank()) +
        scale_y_log10() +
        labs(col= "Institutions in Korea") +
        #facet_wrap(~Field,scales = "free_x") +
        #geom_smooth(method = "lm") +
        scale_y_log10() +
        ylab("Total number of citations from 1996 to 2023") +
        xlab("Total number of papers from 1960 to 2023") +
        scale_x_log10() +
        ggrepel::geom_label_repel(aes(label = inha_researcher), show.legend = F, max.overlaps = 17, fontface = "italic")
        #geom_text(aes(label = inst_name)) +
        #ggrepel::geom_text_repel(aes(label = inst_name))
        
        
        



```




```{r warning=FALSE }
#===============================================================================
#BTC.LineZero.Footer.1.1.0
#===============================================================================
#R markdown citation generator.
#===============================================================================
#RLB.Dependencies:
#   magrittr, pacman, stringr
#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
#BTC.Dependencies:
#   LineZero.Header
#===============================================================================
#Generates citations for each explicitly loaded library.
#=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
str_libraries <- c("r", str_libraries)
for (str_libraries in str_libraries) {
    str_libraries |>
        pacman::p_citation() |>
        print(bibtex = FALSE) |>
        capture.output() %>%
        .[-1:-3] %>% .[. != ""] |>
        stringr::str_squish() |>
        stringr::str_replace("_", "") |>
        cat()
    cat("\n")
}
#===============================================================================
```